\message{ !name(../Tesis.tex)}
\documentclass[11pt,a4paper,twoside]{book}

%
% Definimos  el   comando  \compilaCapitulo,  que   luego  se  utiliza
% (opcionalmente) en config.tex. Quedar_a  mejor si tambi_n se definiera
% en  ese fichero,  pero por  el modo  en el  que funciona  eso  no es
% posible. Puedes consultar la documentaci_n de ese fichero para tener
% m_s  informaci_n. Definimos tambi_n  \compilaApendice, que  tiene el
% mismo  cometido, pero  que se  utiliza para  compilar  _nicamente un
% ap_ndice.
%
%
% Si  queremos   compilar  solo   una  parte  del   documento  podemos
% especificar mediante  \includeonly{...} qu_ ficheros  son los _nicos
% que queremos  que se incluyan.  Esto  es _til por  ejemplo para s_lo
% compilar un cap_tulo.
%
% El problema es que todos aquellos  ficheros que NO est_n en la lista
% NO   se  incluir_n...  y   eso  tambi_n   afecta  a   ficheros  de
% la plantilla...
%
% Total,  que definimos  una constante  con los  ficheros  que siempre
% vamos a querer compilar  (aquellos relacionados con configuraci_n) y
% luego definimos \compilaCapitulo.
\newcommand{\ficherosBasicosTeXiS}{%
TeXiS/TeXiS_pream,TeXiS/TeXiS_cab,TeXiS/TeXiS_bib,TeXiS/TeXiS_cover,%
TeXiS/TeXiS_part%
}
\newcommand{\ficherosBasicosTexto}{%
constantes,guionado,Cascaras/bibliografia,config%
}
\newcommand{\compilaCapitulo}[1]{%
\includeonly{\ficherosBasicosTeXiS,\ficherosBasicosTexto,Capitulos/#1}
}

\newcommand{\compilaApendice}[1]{%
\includeonly{\ficherosBasicosTeXiS,\ficherosBasicosTexto,Apendices/#1}
}

\include{config}

% Paquete de la plantilla

\usepackage{TeXiS/TeXiS}

\setcitestyle{square}


% Incluimos el fichero con comandos de constantes
\include{constantes}%también


\typeout{Copyright Marco Antonio and Pedro Pablo Gomez Martin}

%
% "Metadatos" para el PDF
%
\ifpdf\hypersetup{%
    pdftitle = {\titulo},
    pdfsubject = {Master's Thesis},
    pdfkeywords = {blockchain},
    pdfauthor = {\textcopyright\ \autor},
    pdfcreator = {\LaTeX\ con el paquete \flqq hyperref\frqq},
    pdfproducer = {pdfeTeX-0.\the\pdftexversion\pdftexrevision},
    }
    \pdfinfo{/CreationDate (\today)}
\fi


%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%                        Documento
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
\begin{document}

\message{ !name(Capitulos/Technology.tex) !offset(-57) }
\subsection{Distributed Hash Tables}
A distributed hash table(\emph{DHT}) is a decentralized structure that works very similar to a hash table. Hash tables are used to identify items in a database. The table performs simple mathematical operations generating a random string called hash. The hash acts as a pointer that directs to the data, this allows the user to find data directly instead of looking through the entire database\cite{kaluszka2010distributed}.

In a distributed hash table, any node can use a hash as a key to retrieve data.
This system includes a data structure called ``keyspace'' that is a set of all
possible keys, which is split up across the nodes in the system. The mapping of
the keys is made by another function that describes the distance from one key to
another. All the nodes have and identifier and a set of identifiers pointing to all its neighbours nodes. If a node is removed from the network, only a small
portion of the data must be recovered by other
nodes\cite{kaluszka2010distributed}.

This system makes \emph{DHTs} scalable, fast and robust. It is used by
frameworks such as Tapestry \cite{zhao2004tapestry}, Chord \cite{stoica2001chord}, Kelips
\cite{gupta2003kelips}, Kademlia \cite{maymounkov2002kademlia} and IPFS
\cite{benet2014ipfs}. These platforms are similar in cost and performance if
they are tested in a large enough network. They behave very fast when it comes
to searching for a key through massive networks of nodes\cite{li2004comparing},
that's why it is used by IFPS to create its distributed file system.

\message{ !name(../Tesis.tex) !offset(63) }

\end{document}
