% ---------------------------------------------------------------------
%
% resumen.tex
%
% ---------------------------------------------------------------------
%
% Contiene el cap_tulo del resumen.
%
% Se crea como un cap_tulo sin numeraci_n.
%
% ---------------------------------------------------------------------

\chapter{Abstract}
\cabeceraEspecial{Abstract}

\begin{FraseCelebre}
  \begin{Frase}
    I invent, transform, create and destroy for a living and when I don't like something about the World I change it. 
  \end{Frase}
  \begin{Fuente}
    Rick and Morty -  Dan Harmon, Justin Roiland
  \end{Fuente}
\end{FraseCelebre}

Science publication and peer review raises concerns about fairness, quality,
performance, cost or accuracy. The Open Access movements has been unable to
fulfill all its promises, and middlemen publishers can still impose policies and
concentrate profits. This work, using emerging distributed technologies such as
Blockchain and IPFS, proposes a decentralized publication system for open
science called Decentralized Science\footnote{Available at
  https://decentralized.science}. It provides transparent governance, a
distributed reviewer reputation system, and open access by-design.

\bb{Keywords:} Peer review, reputation network, open acess, blockchain,
Ethereum, IPFS.


\chapter{Resumen}
\cabeceraEspecial{Resumen}

\begin{FraseCelebre}
  \begin{Frase}
    We do what we must because we can.
  \end{Frase}
  \begin{Fuente}
    GLaDOS - Portal.
  \end{Fuente}
\end{FraseCelebre}

El proceso de publicación científica y la revisión por pares generan inquietudes
sobre la equidad, calidad, rendimiento, coste o precision de este. Los movimientos del
\emph{Open Access} no han podido cumplir todas sus promesas, ya que las
editoriales que actúan como 
intermediarios todavía pueden imponer políticas y beneficiarse de este sistema.
Este trabajo, utilizando tecnologías distribuidas emergentes como Ethereum o
IPFS, propone un sistema descentralizado de publicación científica para la
\emph{ciencia libre} llamado Decentralized Science\footnote{Disponible en
  https://decentralized.science}. Proporciona un sistema de gobernanza
tranparente, un sistema de reputación de revisores distribuido y un diseño
totalmente \emph{Open Access}.

\bb{Palabras Clave:} Revisión por pares, red de reputación, open access,
blockchain, Ethereum, IPFS.
\endinput
% Variable local para emacs, para que encuentre el fichero maestro de
% compilaci_n y funcionen mejor algunas teclas r_pidas de AucTeX
%%%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../Tesis.tex"
%%% End:
